Self Regulation Ontology Retest Data Report

### 2017-04-18 SRO_Report.Rmd
playing around with not centering the differences between two measurements

for(i in 1:length(numeric_cols)){
  tmp = match_t1_t2(numeric_cols[i],format='wide')
  tmp = tmp %>% 
    mutate(difference = scale(`2` - `1`))
  t1_2_difference = rbind(t1_2_difference, tmp)
}

t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
```

@@

@@

```{r warning=FALSE, message=FALSE, fig.height=36}
ggplotly(t1_2_difference %>%
           ggplot(aes(dv, difference, label=dv))+
           geom_boxplot()+
           theme_bw()+
           coord_flip()+
           xlab("")+
           ylab("Standardized difference")
)
```

>>>>

for(i in 1:length(numeric_cols)){
  tmp = match_t1_t2(numeric_cols[i],format='wide')
  tmp = tmp %>% 
    # mutate(difference = scale(`2` - `1`))
  mutate(difference = scale(`2` - `1`, center=F))
  t1_2_difference = rbind(t1_2_difference, tmp)
}

t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
str(t1_2_difference)
```

@@

```{r echo=FALSE}
rm(test_comp_date, retest_comp_date, comp_dates)
```

@@

```{r warning=FALSE, message=FALSE, fig.height=36}
ggplotly(t1_2_difference %>%
           ggplot(aes(dv, difference, label=dv))+
           geom_boxplot()+
           theme_bw()+
           xlab("")+
           ylab("Standardized difference")+
           coord_flip())
```
